---
title: "Analyze transmission type influence on fuel efficiency"
author: "Evgeny Kuznetsov"
output:
  html_document:
    keep_md: yes
---

## Synopsis

This is Regression Models Course Project. In this project, we analyze transmission type (AM) influence on fuel efficiency (MPG) 
basing on mtcars dataset. 

## Exploratory analyses

```{r}
data(mtcars) # load data

t.test(mpg ~ am, data = mtcars) # perform t.test
```

We have highly different means in these two groups. See also appendix A for means' graph.

## Regression analyses


```{r}
minimum_fit <- lm(mpg ~ am, data = mtcars) # calculate minimum model

full_fit <- lm(mpg ~ . , data = mtcars) # calculate full model

reduced_fit <- step(full_fit, trace = 0) # calculate reduced model

AIC(minimum_fit, full_fit, reduced_fit) # calculate An Information Criterion
```

```{r echo=FALSE}
# hidden block to not mess up text
aic_val <- round(AIC(reduced_fit), 2)
sqr_val <- round(100*summary(reduced_fit)$r.squared, 2)
asqr_val <- round(100*summary(reduced_fit)$adj.r.squared, 2)
res <- round((confint(reduced_fit)[4,2] + confint(reduced_fit)[4,1]) / 2, 2)
int <- round((confint(reduced_fit)[4,2] - confint(reduced_fit)[4,1]) / 2, 2)
```

Our strategy is to use model with minimum on An Information Criterion. Reduced model has minimum on AIC - `r aic_val`. So, let's use this model.

```{r}
summary(reduced_fit)
```

Our residual diagnose for chosen model that it explains `r sqr_val`% of variance with an adjustment to `r asqr_val`%. See also appendix B for residuals plots.


```{r}
confint(reduced_fit) # take confidence interval
```


Our quantitive value for manual transimission improvement is `r res` ± `r int` with 95% confidence interval. 


## Executive Summary

After analyses we conclude the following:

* manual transmission is better for MPG
* manual transmission increase MPG by 2.94 ± 2.89 with 95% confidence interval


\newpage

## Appendix A

```{r}
boxplot(mpg ~ factor(am, labels = c("Automatic", "Manual")), data = mtcars, 
  col = c("red", "blue"), main = "Overall means", xlab = "Transmission",
  ylab = "Miles per Gallon") 
points(mpg ~ factor(am, labels = c("Automatic", "Manual")), data = mtcars)
legend("topleft", c("Automatic", "Manual"), lty = 1, col = c("red", "blue"))
```

\newpage

## Appendix B

```{r}
par(mfrow = c(2, 2))
plot(reduced_fit)
```

